---
title: "Homework#5"
author: "Jim Holdnack"
date: "February 10, 2019"
output: html_document
---
###### Open and clean file y2016
1. import file -- I set the working directory to file repository and used read.table. I cleaned up the import so variables were named and had correct format
2. Display the summary and structure of df-- i used summary str
3. find mispelled name---I used grep to identify the row and then printed the row for column name.
d. Upon finding the misspelled name, please remove this particular observation I used file = and subtract specific row with erroneous name

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
getwd()
setwd("/Users/jhold/Desktop/homework5")
library(tidyverse)
library(readr)
df <- read.table("/Users/jhold/Desktop/homework5/yob2016.txt", sep = ';' )
df$name <- as.character(df$V1)
df$sex  <- df$V2
df$Frequency <- df$V3
df <- df[-c(1,2,3)]
str(df)
summary(df)
grep('yyy',df$name)
df$name[212]
y2016 <-df[-212,]
str(y2016)
```
## Data Merging 
1. imported the y2015 file using read.table and did clean-up like part 1 though I had to separate by comma rather than semi-colon
2. Display the last ten rows in the dataframe I used tail command for 10 rows. All the names are boys names and all have exactly 5 as frequency of use, and all are "z" names
c. Merge y2016 and y2015 by your Name column. I merged on both name and sex to make for a cleaner merge. I used the na omit function to get rid og missing data rows - I used head 100 to make sure no missing data was present

```{r, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
df2 <- read.table("/Users/jhold/Desktop/homework5/yob2015.txt", sep = ',')
df2$name <- as.character(df2$V1)
df2$sex  <- df2$V2
df2$Frequency <- df2$V3
y2015 <- df2[-c(1,2,3)]
tail(y2015,10)
nd1 <- merge(y2016, y2015, union("name", "sex"), all=TRUE)
head(nd1,100)
nd1$missx <-is.na(nd1$Frequency.x)
final <- na.omit(nd1)
str(final)
final <- final[c(1,2,3,4)]
head(final,100)
```
