---
title: "Homework3v7"
author: "Jim Holdnack"
date: "January 28, 2019"
output:  
  html_document:
    keep_md: true
---
# 1 

a. find current directory: use pwd 
   - jhold@DESKTOP-BVT54UQ MINGW64 ~ $ pwd = /c/Users/jhold
b. change directory to where I want to clone git use cd: 
     $ cd /c/Users/jhold/Desktop
c. new directory
      jhold@DESKTOP-BVT54UQ MINGW64 ~/Desktop
d. initialize new local directory to clone git repo: use git init
      git init /c/Users/jhold/Desktop/Caeser0301
      Initialized empty Git repository in C:/Users/jhold/Desktop/Caeser0301/.git/
e. clone to my local repository: use git clone
       jhold@DESKTOP-BVT54UQ MINGW64 ~/Desktop/Caeser0301 (master)
       git clone https://github.com/awesomedata/awesome-public-datasets 
          Cloning into 'awesome-public-datasets'...
          remote: Enumerating objects: 76, done.
          remote: Counting objects: 100% (76/76), done.
          remote: Compressing objects: 100% (37/37), done.
          remote: Total 1692 (delta 49), reused 66 (delta 39), pack-reused 1616
          Receiving objects: 100% (1692/1692), 627.23 KiB | 4.61 MiB/s, done.
          Resolving deltas: 100% (1003/1003), done.
f. change directory and list files: use ls
        jhold@DESKTOP-BVT54UQ MINGW64 ~/Desktop/Caeser0301/awesome-public-datasets/Datasets (master)
         $ ls
        titanic.csv.zip



# 2 Data Summary (20 points): From this aforementioned cloned repo, please extract


```{r echo=TRUE}
knitr::opts_chunk$set(echo = TRUE)
# Homework Question 2a,b,c
# load tidyverse library to read .csv files
library(tidyverse)
getwd()
#read .csv file from local director where .md file is saved
df <- read_csv(file="titanic.csv")
#check contents of file
head(df)
str(df)
# create table of sex counts
sexn <- df$Sex
table(sexn)
# create a vector of means using sappy missing values in age cause it ti return NA need to drop those in calculation
v1 <- df[c(2,6,10)]
sapply(v1,mean, na.rm=TRUE)
```

## Function Building (30 points): You research sleep and just got your first data set.

```{r }
# Homework Question 3
# load tidyverse library to read .csv files
library(tidyverse)
getwd()
#read .csv file from local director where .md file is saved
sdat <- read_csv(file="sleep_data_01.csv")
#check contents of file
head(sdat)
str(sdat)
# create a function to return median, min, max, range, mean sd for 2,12,15, make sure missing not included
new_df_descriptive <- function(data.frame) {
  a <- sdat$Age
  b <- sdat$RSES
  c <- sdat$Duration
  a1 <- median(a, na.rm=TRUE) 
  c1 <- min(c, na.rm=TRUE)
  c2 <- max(c, na.rm=TRUE)
  c3 <- c2-c1
  b1 <- mean(b,na.rm=TRUE)/5
  b2 <- sd(b,na.rm=TRUE)/5
  x1 <- c("MedianAge", "SelfEsteem", "SE_SD", "DurationRange")
  x2 <- c(a1,b1,b2,c3)
  x3 <- c("statistic","value")
  report <- cbind(x1, x2)
  # i tried data.frame and it never works not sure what to do
  return(report)
}
# apply function to data
new_df_descriptive(sdat)
```

## FiveThirtyEight Data (30 points) & Data Summary (30 points):

```{r}
# Homework Question 4
#read data file from local director where .md file is saved
library(fivethirtyeight)
attach(college_recent_grads)
class(college_recent_grads)
df <- college_recent_grads #assigning 22nd dataset to df
head(df)
str(df) #gives information about data set variable names and observations
library(fivethirtyeight)
attach(college_recent_grads)
df <- college_recent_grads
names(df) # gives variable names for dataset
dim(df)# gives nuber of rows and columns
ncol(df) # gives number of columns
mc <- college_recent_grads$major_category
major_count <- sapply(mc, function(x) length(unique(x))) # save counts of majors to a new vector

plot(major_count)
write.csv(df, file = "college.csv",row.names=FALSE)
```

